\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{natbib}
\usepackage{geometry}
\geometry{margin=2.5cm}

\title{QuantEvoLoop: LLM-Guided Multi-Agent Evolutionary Framework\\
       for Quantitative Strategy Optimization}

\author{
  Wenjie Huang\textsuperscript{1} \and
  Co-Author\textsuperscript{2} \\[0.5em]
  \textsuperscript{1}Shenzhen University \\
  \textsuperscript{2}Institution Name \\
  \texttt{email@example.com}
}

\date{\today}

\begin{document}

\maketitle

% ============================================================
\begin{abstract}
We present QuantEvoLoop, a novel framework that leverages Large Language Model
(LLM) agents as code mutation engines within a multi-agent evolutionary loop
for automated quantitative trading strategy optimization. Unlike traditional
hyperparameter optimizers (Optuna, Hyperopt) that search over fixed parameter
spaces, QuantEvoLoop performs \emph{structural} mutations on strategy code,
guided by a 5-layer statistical gate pipeline (PSR, Bootstrap CI, Walk-Forward,
Holdout OOS) to rigorously prevent overfitting. We introduce three key
innovations: (1)~Agent-as-Backend architecture that reuses production-grade
CLI agents (Claude Code, Codex, Qoder CLI) for AST-level code understanding;
(2)~UCB1 Multi-Armed Bandit for adaptive mutation type selection; and
(3)~Cross-Campaign Knowledge Accumulation that transfers optimization insights
across strategy campaigns. Experimental results on Freqtrade backtests
demonstrate \textbf{XX\%} improvement in risk-adjusted returns over baseline
strategies across \textbf{N} crypto pairs.
\end{abstract}

% ============================================================
\section{Introduction}
\label{sec:intro}

Quantitative trading strategies require continuous adaptation to evolving
market regimes. Traditional approaches rely on manual parameter tuning or
grid-search hyperparameter optimization, both of which suffer from:
\begin{itemize}
  \item \textbf{Fixed search spaces}: Hyperopt/Optuna only optimize within
        pre-defined parameter ranges.
  \item \textbf{No structural innovation}: They cannot introduce new indicators,
        filters, or exit conditions.
  \item \textbf{Overfitting risk}: Without rigorous out-of-sample validation,
        optimized parameters often degrade in live trading.
\end{itemize}

Recent advances in LLM-based code generation suggest a paradigm shift:
treating strategy \emph{code} as a living organism that can be diagnosed,
mutated, and evolved. This paper introduces QuantEvoLoop...

% ============================================================
\section{Related Work}
\label{sec:related}

\subsection{Evolutionary Algorithms in Finance}
Population-Based Training (PBT) has been applied to...

\subsection{LLM for Code Generation}
Recent work (Chen et al., 2023; Jimenez et al., 2024) demonstrates...

\subsection{Statistical Validation in Quantitative Finance}
Bailey and L\'{o}pez de Prado (2014) introduced the Probabilistic Sharpe
Ratio (PSR) to address...

% ============================================================
\section{Methodology}
\label{sec:method}

\subsection{Architecture Overview}
QuantEvoLoop consists of five core modules:
\begin{enumerate}
  \item \textbf{Diagnosis Engine}: 7-type weakness detector (MFE giveback,
        stop-loss dominance, directional asymmetry, etc.)
  \item \textbf{Hypothesis Generator}: Maps weaknesses to structured mutation
        hypotheses (what, why, expected effect, falsification criteria).
  \item \textbf{Mutation Engine}: Agent-as-Backend using Claude Code / Codex /
        Qoder CLI for AST-level code editing.
  \item \textbf{Evaluation Pipeline}: 5-layer statistical gate cascade.
  \item \textbf{Selection Mechanism}: UCB1 bandit + tournament selection.
\end{enumerate}

\subsection{5-Layer Statistical Gate Pipeline}
Every candidate strategy must pass 5 sequential gates:
\begin{align}
  G_1&: \text{Train regression } (\hat{S}_{train} \geq S_{champ,train} \times 0.95) \\
  G_2&: \text{Hard constraints (risk, trade count, overfit gap)} \\
  G_3&: \text{Composite score } > 0 \\
  G_4&: \text{PSR}(\hat{S}_{test}) > 0.85 \text{ and Bootstrap CI}_{lo} > 0 \\
  G_5&: \text{Walk-Forward consistency + Holdout OOS gate}
\end{align}

\subsection{UCB1 Multi-Armed Bandit}
Mutation types are treated as bandit arms...
\begin{equation}
  \text{UCB1}(a) = \bar{r}_a + c \sqrt{\frac{\ln T}{N_a}}
\end{equation}

\subsection{Cross-Campaign Knowledge Accumulation}
...

% ============================================================
\section{Experimental Setup}
\label{sec:experiments}

\subsection{Datasets}
We evaluate on cryptocurrency pairs from Binance USD-M futures:
\begin{itemize}
  \item \textbf{BTC/USDT}, \textbf{ETH/USDT} (2021-01-01 to 2026-01-01, 1h candles)
  \item Train: 2022-01-01 to 2024-07-01 (30 months)
  \item Test: 2024-07-01 to 2026-01-01 (18 months)
  \item Holdout: 2021-01-01 to 2022-01-01 (12 months, cross-regime validation)
  \item Walk-Forward: 3 overlapping folds from train period (10-month spans)
\end{itemize}

\subsection{Baselines}
\begin{itemize}
  \item \textbf{Manual Baseline}: Hand-crafted EMA+RSI trend-following strategy
        (\texttt{examples/sample\_strategy.py})
  \item \textbf{Optuna}: Hyperparameter TPE sampler over EMA periods, RSI thresholds,
        stoploss, and ROI parameters (200 trials)
  \item \textbf{Freqtrade Hyperopt}: Bayesian optimization with default settings (500 iterations)
  \item \textbf{QuantEvoLoop (ours)}: Full pipeline with Claude Code backend,
        3 parallel lanes, 20 generations
\end{itemize}

\subsection{Experimental Configuration}
\begin{table}[h]
\centering
\caption{QuantEvoLoop experimental hyperparameters}
\label{tab:config}
\begin{tabular}{ll}
\toprule
Parameter & Value \\
\midrule
Backend & Claude Code CLI (max\_turns=15, timeout=300s) \\
Parallel Lanes & 3 \\
Max Generations & 20 \\
Mutation Types & 8 (EXIT\_TIGHTEN, EXIT\_LOOSEN, NEW\_FILTER, BOX\_FILTER, \\
               & COOLDOWN, PARAM\_TUNE, GENERAL\_TUNE, ENTRY\_REFINE) \\
Selection & UCB1 Bandit + Tournament \\
PSR Threshold (test) & $\geq 0.85$ \\
Bootstrap CI (test) & $\geq 0.70$ \\
Max DD Ceiling & $\leq 1.25\times$ champion DD \\
Min Trades & $\geq 50$ \\
Walk-Forward Folds & 3 overlapping \\
Budget & \$50 USD \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Metrics}
Sharpe Ratio, CAGR, Maximum Drawdown, Win Rate, Profit Factor, Sortino Ratio.

% ============================================================
\section{Results}
\label{sec:results}

\begin{table}[h]
\centering
\caption{Comparison of strategy optimization methods on BTC/USDT}
\label{tab:results}
\begin{tabular}{lccccc}
\toprule
Method & Sharpe & CAGR & MaxDD & WinRate & Trades \\
\midrule
Manual Baseline     & 0.XX & XX\% & XX\% & XX\% & XXX \\
Optuna              & 0.XX & XX\% & XX\% & XX\% & XXX \\
Hyperopt            & 0.XX & XX\% & XX\% & XX\% & XXX \\
\textbf{QuantEvoLoop} & \textbf{0.XX} & \textbf{XX\%} & \textbf{XX\%} & XX\% & XXX \\
\bottomrule
\end{tabular}
\end{table}

% ============================================================
\section{Discussion}
\label{sec:discussion}

\subsection{Mutation Type Analysis}
...

\subsection{Cost Efficiency}
...

\subsection{Limitations}
...

% ============================================================
\section{Conclusion}
\label{sec:conclusion}

We presented QuantEvoLoop, a novel framework that...

% ============================================================
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem[Bailey and L\'{o}pez de Prado(2014)]{bailey2014}
Bailey, D.H. and L\'{o}pez de Prado, M.
``The deflated Sharpe ratio: Correcting for selection bias, backtest overfitting, and non-normality.''
\emph{Journal of Portfolio Management}, 40(5):94--107, 2014.

\bibitem[Efron and Tibshirani(1993)]{efron1993}
Efron, B. and Tibshirani, R.J.
\emph{An Introduction to the Bootstrap}.
Chapman \& Hall, 1993.

\bibitem[Pardo(2008)]{pardo2008}
Pardo, R.
\emph{The Evaluation and Optimization of Trading Strategies}.
Wiley, 2nd edition, 2008.

\end{thebibliography}

\end{document}
